\begin{definition}
    A morphism $\pi:X\to Y$ of schemes is said to be \define{separated} if the diagonal morphism $\Delta: X\to X\times_Y X$ is a closed immersion.
    \begin{equation*}
        \xymatrix{
            X\ar[rd]^\Delta\ar@/^/[rrd]^{\id_X}\ar@/_/[rdd]_{\id_X} & & \\
            & X\times_Y X\ar[r]^-{p_1}\ar[d]_{p_2} & X\ar[d]^{\pi}\\
            & X\ar[r]_\pi & Y
        }
    \end{equation*}
\end{definition}

\begin{definition}
    A morphism $\pi: X\to Y$ is said to be \define{universally closed} if it is closed as a continuous map on the underlying topological spaces and for every morphism $Y'\to Y$, the map obtained by \emph{base extension} $X\times_Y Y'\to Y'$ is also closed.
\end{definition}

\begin{definition}
    A morphism $\pi: X\to Y$ is said to be \define{proper} if it is separated, of finite type and universally closed.
\end{definition}

Since a complete proof of the following is not provided in the text, I reproduce it here.

\begin{corollary}[Hartshorne, II.4.6]
    Assume that all schemes are noetherian in the following statements.
    \begin{enumerate}[label=(\alph*)]
        \item Open and closed immersions are separated.
        \item A composition of two separated morphisms is seprated. 
        \item Separated morphisms are stable under base extension.
        \item If $\pi: X\to Y$ and $\pi': X'\to Y'$ are separated morphisms of schemes over a base scheme $S$, then the \define{product morphism} $\pi\times\pi': X\times_S X'\to Y\times_S Y'$ is also separated.
        \item If $\pi: X\to Y$ and $\varphi: Y\to Z$ are two morphisms and if $\varphi\circ\pi$ is separated, then $\pi$ is separated.
        \item A morphism $\pi: X\to Y$ is separated if and only if $Y$ can be covered by open subsets $V_i$ such that $\pi^{-1}V_i\to V_i$ is separated for each $i$.
    \end{enumerate}
\end{corollary}
\begin{proof}
\begin{enumerate}[label=(\alph*)]
\item We show more generally that ``a monomorphism of schemes is separated''. Let $Y\into X$ be a monomorphism in $\mathfrak{Sch}_\Z$. Then, the fiber product $Y\times_X Y$ is precisely $Y$, given by the following diagram. 
\begin{equation*}
    \xymatrix {
    Z\ar@/^/[rrd]\ar@/_/[rdd] & & \\
        &Y\ar[d]_\id\ar[r]^\id & Y\ar@{^(->}[d]\\
        &Y\ar@{^(->}[r] & X
    }
\end{equation*}
Since $Y\into X$ is a monomorphism, the two maps $Z\to Y$ in the above diagram must be the same and it follows that $Y = Y\times_X Y$. Hence, the diagonal morphism $\Delta: Y\to Y\times_X Y$ is the identity map, whence is a closed immersion.

\item We use the valuative criterion. Let $R$ be a DVR and $K$ its fraction field. Let $U = \Spec K$ and $T = \Spec R$ and suppose $\pi: X\to Y$ and $\varphi: Y\to Z$ are separated. Let there be a commutative diagram 
\begin{equation*}
    \xymatrix {
        U\ar[r]\ar[dd] & X\ar[d]\\
        & Y\ar[d]\\
        T\ar[r] & Z.
    }
\end{equation*}
Suppose there are two lifts $\psi_1,\psi_2: T\to X$ making the diagram commute. Then, $\pi\circ\psi_1 = \pi\circ\psi_2$ since $Y\to Z$ is separated. Finally, since $X\to Y$ is separated, we must have $\psi_1 = \psi_2$. This shows that $X\to Z$ is separated.

\item This is done in the book. 

\item The same idea as in (b) works. Not writing this up because the diagram is too complicated to draw and I'm too lazy.

\item Again, begin with a commutative diagram 
\begin{equation*}
    \xymatrix {
        U\ar[r]\ar[d] & X\ar[d]\\
        T\ar[r]\ar[rd] & Y\ar[d]\\
        & Z
    }
\end{equation*}
and suppose there are two lifts $\psi_1,\psi_2: T\to X$ making the diagram commute. Since $X\to Z$ is separated, we must have that $\psi_1 = \psi_2$. Hence, $X\to Y$ is separated.

\item 
\end{enumerate}
\end{proof}