%!TEX root = ./CV.tex

\begin{rubric}{Service}
	\entry*[2022--2024] \textbf{Teaching Assistantship} \hfill \emph{IIT Bombay}

	   2024 \quad \textbf{MA 105 (Calculus)} \hfill \emph{Instructor: Prof. Swapneel Mahajan}

	   2024\quad \textbf{MA 419 S (Basic Algebra)} \hfill \emph{Instructor: Prof. Shripad Garge}

	   2024\quad \textbf{MA 414 S (Algebra I: Galois Theory)} \hfill \emph{Instructor: Prof. Shripad Garge.}

	   2024 \quad \textbf{MA 414 (Algebra I: Galois Theory)} \hfill  \emph{Instructor: Prof. Saurav Bhaumik}

	   2023 \quad \textbf{MA 106 (Linear Algebra)} \hfill \emph{Instructor: Prof. Dipendra Prasad}

	   2023 \quad \textbf{MA 111 (Calculus II)} \hfill \emph{Instructor: Prof. Preeti Raman}
	   
	   2022 \quad \textbf{CS 228 (Logic for CS)} \hfill  \emph{Instructor: Prof. Krishna S.}
	   
	   2022 \quad \textbf{MA 106 (Linear Algebra)} \hfill \emph{Instructor: Prof. Gopal Krishna Srinivasan}

	    Responsible for conducting problem solving sessions for a batch of students throughout the semester, helping them clear conceptual doubts through personal interaction, and grading papers. 
		Created \LaTeX ed \href{https://swayamchube.github.io/notes}{notes} which were referred to repeatedly by multiple students. Also conducted various ``cram sessions'' for students before major exams.

		In some cases, I have also been involved in making problems for the tests.

	\entry*[2023, 2024] \textbf{Mentor, Summer of Science}

		Guided students interested in Abstract Algebra, Topology, Combinatorics, and Real Analysis by creating an action plan, recommending resources, clearing doubts, having discussions, and reviewing their reports	

	\entry*[] \textbf{Various Expository Notes}

		Over the past year, I have written quite a few notes and mini-expositions on topics that I found interesting. They can be found \href{https://swayamchube.github.io/notes}{here}.
\end{rubric}