\subsection{Eakin-Nagata Theorem}

\begin{theorem}[Formanek]\thlabel{thm:formanek}
    Let $A$ be a ring, and $B$ a finitely generated faithful $A$-module. Suppose the set of $A$-submodules $\Sigma = \left\{\fraka B\colon \fraka\noreq A\right\}$ has the ascending chain condition, then $A$ is noetherian.
\end{theorem}
\begin{proof}
    It suffices to show that $B$ is a noetherian $A$-module since it is finitely generated and faithful. Suppose not. Then consider the collection 
    \begin{equation*}
        \Gamma = \left\{\fraka B\colon \fraka\noreq A,~B/\fraka B\text{ is a non-noetherian }A\text{-module}\right\},
    \end{equation*}
    which contains $(0)$ and hence is non-empty. Since $\Sigma$ has the ascending chain condition, so does $\Gamma$, whence, it contains a maximal element $\fraka B$. 

    Replacing $B$ by $B/\fraka B$, we see that $B$ is a non-noetherian $A$-module. This may not be faithful and hence, replace $A$ by $A/\Ann_A(B)$. Then, $B$ is a finite, non-noetherian, faithful $A$-module such that for every ideal $0\ne\fraka\nor A$, $B/\fraka B$ is a noetherian $A$-module.

    Next, set 
    \begin{equation*}
        \frakM = \left\{N\le B\colon B/N\text{ is a faithful }A\text{-module}\right\},
    \end{equation*}
    which is non-empty, since $\{0\}\in\frakM$. Suppose $B$ is generated as an $A$-module by $b_1,\dots, b_n$. It is not hard to argue that 
    \begin{equation*}
        N\in\frakM\iff \forall~a\in A\setminus\{0\},~\{ab_1,\dots, ab_n\}\not\subseteq N.
    \end{equation*}
    It follows that every chain in $\frakM$ has a maximal element and hence Zorn's Lemma applies to furnish a maximal element $N_0\in\Gamma$.

    If $B/N_0$ is a noetherian $A$-module, then $A$ is noetherian since $B/N_0$ is faithful and finite. If not, replace $B$ with $B/N_0$, which is still a finite faithful $A$-module and satisfies: 
    \begin{enumerate}[label=(\arabic*)]
        \item $B$ is a non-noetherian $A$-module. 
        \item for any ideal $0\ne\fraka\noreq A$, $B/\fraka B$ is a noetherian $A$-module. 
        \item for any submodule $0\ne N$ of $B$, $B/N$ is not faithful as an $A$-module.
    \end{enumerate}

    Now, let $N$ be a non-zero submodule of $B$. Due to (3), there is a $0\ne a\in A$ such that $aB\subseteq N$. Due to (2), $B/aB$ is a noetherian $A$-module with $N/aB$ as a submodule. Thus, $N/aB$ is a noetherian, in particular, a finite $A$-module. Since $aB$ is also finite as an $A$-module, we have that $N$ is a finite $A$-module. Hence, $B$ is a noetherian $A$-module, which is absurd. This completes the proof.
\end{proof}

\begin{theorem}[Eakin-Nagata]\thlabel{thm:eakin-nagata}
    Let $A\subseteq B$ be an extension of rings such that $B$ is a finite $A$-module. If $B$ is a noetherian ring, then so is $A$.
\end{theorem}
\begin{proof}
    Note that $B$ is a finite, faithful $A$-module, since $1\in B$. The conclusion follows from \thref{thm:formanek}.
\end{proof}